%%
%% This is file `kth-abs.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% kthesis.dtx  (with options: `abstract')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from kth-abs.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file kthesis.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
\begin{abstract}
  In this paper a scenario of one evader being chased  by multiple pursuers in two specific simulation environments is studied. The simulation environments are divided into an open area without obstacles and a closed area with obstacles. In the open
area a fairly accurate system of dynamics are implemented for both pursuers and evader. The Virtual Vehicle Approach is used to provide a reference trajectory for the pursuers to follow in order to catch the evader. The main purpose of this thesis is to find a decentralized robust
control method for the dynamics of the pursuers. In the closed area, the line of sight and field of view
are introduced and the solution to the Minimum time UGV surveillance problem and the Centroidal
Voronoi partitions. Different
capturing strategies, encirclement and one-on-one chase, are both studied and compared. The
numerical implementation and the resulting simulation are presented and analyzed. Conclusion on
the optimal formation for the multiple pursuers is made.
\end{abstract}
\endinput
%%
%% End of file `kth-abs.tex'.
